---
title: "Final models traits - forest cover at local and landscape scale"
author: "Melina Leite"
date: "`r format(Sys.time(), '%d de %B de %Y')`"
output:
  rmdformats::readthedown:
    highlight: kate
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
    fig_heigth: 20
  pdf_document:
    highlight: tango
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = T, warning = F, fig.align = "center", message = F,
  error = F, cache = T, fig.pos="H")

library(knitr)
library(tidyverse); library(cowplot); library(patchwork); library(ggrepel)
library(lme4); library(bbmle); library(broom.mixed)
theme_set(theme_cowplot())
```

Loading auxiliary function for R2 calculations
```{r}
source("r2_auxiliary_function.R")
```

Loading data
```{r}
load("datasets.Rdata")
load("models_outputs/models_combined.Rdata") # saved models results this script
load("models_outputs/models_traits.Rdata") # saved models results separate
load("models_outputs/models_traits_nointeraction.Rdata") # saved models results separate
```


# Combined traits models

```{r, eval=F}
mhigh.spe <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400*lbody_size + 
                    forest_site400*nest +
                    forest_site400*diet + 
                    forest_site400*lower_stratum +
                    forest_land*lbody_size + 
                    forest_land*nest + 
                    forest_land*diet +
                    forest_land*lower_stratum + 
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=high.spe,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))


mlow.spe <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400*lbody_size + 
                    forest_site400*nest +
                    forest_site400*diet + 
                    forest_site400*lower_stratum +
                    forest_land*lbody_size + 
                    forest_land*nest + 
                    forest_land*diet +
                    forest_land*lower_stratum + 
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=low.spe,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))


mhigh.gen <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400*lbody_size + 
                    forest_site400*nest +
                    forest_site400*diet + 
                    forest_site400*lower_stratum +
                    forest_land*lbody_size + 
                    forest_land*nest + 
                    forest_land*diet +
                    forest_land*lower_stratum + 
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=high.gen,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))


mlow.gen <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400*lbody_size + 
                    forest_site400*nest +
                    forest_site400*diet + 
                    forest_site400*lower_stratum +
                    forest_land*lbody_size + 
                    forest_land*nest + 
                    forest_land*diet +
                    forest_land*lower_stratum + 
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=low.gen,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))
```

# Local and landscape forest cover effects

Comparing effect sizes and 95% IC for fixed effects forest cover a local and landscape scale for each assemblage.

```{r, echo=F}
fhigh.spe <- tidy(mhigh.spe, effects = "fixed") %>% select(-effect)
fhigh.gen <- tidy(mhigh.gen, effects = "fixed") %>% select(-effect)
flow.spe  <- tidy(mlow.spe, effects = "fixed") %>% select(-effect)
flow.gen  <- tidy(mlow.gen, effects = "fixed") %>% select(-effect)
```

```{r, echo=F}
fc <- bind_rows(list(High.Specialists=fhigh.spe, 
                     Low.Specialists=flow.spe, 
                     High.Generalists=fhigh.gen,
                     Low.Generalists =flow.gen), .id= "model") %>%
  separate(model, c("matrix", "habitat"), remove = F) %>%
  filter(term %in% c("forest_land", "forest_site400")) %>%
  arrange(habitat, matrix,term) %>%
  mutate(iclow = estimate - 1.96*std.error,
         icup = estimate + 1.96*std.error, 
         habitat = fct_relevel(habitat, "Specialists", "Generalists"),
         term = fct_recode(term, Landscape = "forest_land", Local = "forest_site400")) %>%
  mutate(term = fct_relevel(term, "Local", "Landscape"),
         matrix = fct_relevel(matrix, "High", "Low"))

fig.forest <- fc %>%
  ggplot(aes(x=estimate, y=matrix, col=matrix)) + geom_point() + 
  geom_errorbarh(aes(xmin=iclow, xmax=icup), height=0) +
  facet_grid(cols= vars(term), rows=vars(habitat), switch = "y") +
  geom_vline(xintercept = 0, linetype="dashed", col="grey") +
  scale_color_manual(name="  Matrix \n  quality ",
                     values=c("darkgreen", "sandybrown")) +
 theme(text = element_text(size=12),
        axis.text = element_text(size=12),
        strip.text.x = element_text(size=12, margin=margin(t=2,b=3)),
        strip.text.y = element_text(size=12, margin=margin(r=2,l=3)),
       legend.position = c(0.89, 0.2),
       plot.title = element_text(hjust = 0.5),
       legend.box.background = element_rect(fill="snow2", color="snow2"),
       axis.text.y = element_blank(),
       axis.line.y = element_blank(),
       axis.ticks.y = element_blank()) +
  xlab("Effect size") + ylab("")+
  ggtitle("Forest cover")
fig.forest
```

```{r, echo=F, results="hide"}
jpeg("figures/forest_cover_effectsize.jpg", width=16, height = 10, units="cm", res=150)
fig.forest
dev.off()
```

Estimating effect sizes (slopes) of local and landscape forest cover for each species in each assemblage. Estimates include fixed effects slopes and random slopes of the species.

```{r, echo=F}
######
# slope estimate for each species considering random and fixed effects
vhs <- coef(mhigh.spe)$sp
vls <- coef(mlow.spe)$sp
vhg <- coef(mhigh.gen)$sp
vlg <- coef(mlow.gen)$sp


## high specialists
vhigh.spe <- high.spe %>% select(sp, lbody_size, nest, diet, lower_stratum) %>% distinct()

sera <- model.matrix(~lbody_size+nest+diet+lower_stratum, data=vhigh.spe)

opa <- sera %>% as.data.frame() %>%
  mutate(forest_site400 = 1,
         forest_land = 1,
         `forest_site400:lbody_size` = 1,
         `forest_site400:nestclosed`= nestclosed,
         `forest_site400:nestopen_semi` = nestopen_semi,
         `forest_site400:dietinsectivorous` =  dietinsectivorous,
          `forest_site400:dietonivorous` = dietonivorous,
         `forest_site400:lower_stratum` =     1, 
          `lbody_size:forest_land` = 1,         
         `nestclosed:forest_land` = nestclosed,
         `nestopen_semi:forest_land` = nestopen_semi,       
         `dietinsectivorous:forest_land` = dietinsectivorous,
         `dietonivorous:forest_land`  =   dietonivorous,
         `lower_stratum:forest_land`= 1) 
upis <- opa %>% select(colnames(vhs))
#names(upis) == names(vhs)

ult <- upis*vhs

vhs.loc <- ult[,c(2,3,10:15)]
vhs$local <- rowSums(vhs.loc)
vhs.land <- ult[, c(9,16:21)]
vhs$land <- rowSums(vhs.land)

## low specialists
vlow.spe <- low.spe %>% select(sp, lbody_size, nest, diet, lower_stratum) %>% distinct()

sera <- model.matrix(~lbody_size+nest+diet+lower_stratum, data=vlow.spe)

opa <- sera %>% as.data.frame() %>%
  mutate(forest_site400 = 1,
         forest_land = 1,
         `forest_site400:lbody_size` = 1,
         `forest_site400:nestclosed`= nestclosed,
         `forest_site400:nestopen_semi` = nestopen_semi,
         `forest_site400:dietgranivorous` =  dietgranivorous,
         `forest_site400:dietinsectivorous` =  dietinsectivorous,
         `forest_site400:lower_stratum` = 1, 
         `lbody_size:forest_land` = 1,         
         `nestclosed:forest_land` = nestclosed,
         `nestopen_semi:forest_land` = nestopen_semi,       
         `dietinsectivorous:forest_land` = dietinsectivorous,
         `dietgranivorous:forest_land` = dietgranivorous,
         `lower_stratum:forest_land`= 1) 
upis <- opa %>% select(colnames(vls))
#colnames(upis) == colnames(vls)

ult <- upis*vls

vls.loc <- ult[,c(2,3,10:15)]
vls$local <- rowSums(vls.loc)
vls.land <- ult[, c(9,16:21)]
vls$land <- rowSums(vls.land)


## high specialists
vhigh.gen <- high.gen %>% select(sp, lbody_size, nest, diet, lower_stratum) %>% distinct()

sera <- model.matrix(~lbody_size+nest+diet+lower_stratum, data=vhigh.gen)

opa <- sera %>% as.data.frame() %>%
  mutate(forest_site400 = 1,
         forest_land = 1,
         `forest_site400:lbody_size` = 1,
         `forest_site400:nestclosed`= nestclosed,
         `forest_site400:nestopen_semi` = nestopen_semi,
         `forest_site400:dietgranivorous` =  dietgranivorous,
         `forest_site400:dietinsectivorous` =  dietinsectivorous,
         `forest_site400:dietnectarivorous` =  dietnectarivorous,
         `forest_site400:dietonivorous` = dietonivorous,
         `forest_site400:lower_stratum` =     1, 
         `lbody_size:forest_land` = 1,         
         `nestclosed:forest_land` = nestclosed,
         `nestopen_semi:forest_land` = nestopen_semi,
         `dietgranivorous:forest_land` = dietgranivorous,
         `dietinsectivorous:forest_land` = dietinsectivorous,
         `dietnectarivorous:forest_land` = dietnectarivorous,
         `dietonivorous:forest_land`  =   dietonivorous,
         `lower_stratum:forest_land`= 1) 
upis <- opa %>% select(colnames(vhg))
#names(upis) == names(vhg)

ult <- upis*vhg

vhg.loc <- ult[,c(2,3,10:15)]
vhg$local <- rowSums(vhg.loc)
vhg.land <- ult[, c(9,16:21)]
vhg$land <- rowSums(vhg.land)

## low specialists
vlow.gen <- low.gen %>% select(sp, lbody_size, nest, diet, lower_stratum) %>% distinct()

sera <- model.matrix(~lbody_size+nest+diet+lower_stratum, data=vlow.gen)

opa <- sera %>% as.data.frame() %>%
  mutate(forest_site400 = 1,
         forest_land = 1,
         `forest_site400:lbody_size` = 1,
         `forest_site400:nestclosed`= nestclosed,
         `forest_site400:nestopen_semi` = nestopen_semi,
         `forest_site400:dietgranivorous` =  dietgranivorous,
         `forest_site400:dietinsectivorous` =  dietinsectivorous,
         `forest_site400:dietnectarivorous` =  dietnectarivorous,
         `forest_site400:dietonivorous` =  dietonivorous,
         `forest_site400:lower_stratum` = 1, 
         `lbody_size:forest_land` = 1,         
         `nestclosed:forest_land` = nestclosed,
         `nestopen_semi:forest_land` = nestopen_semi,
         `dietgranivorous:forest_land` = dietgranivorous,
         `dietinsectivorous:forest_land` = dietinsectivorous,
         `dietnectarivorous:forest_land` = dietnectarivorous,
         `dietonivorous:forest_land` =dietonivorous,
         `lower_stratum:forest_land`= 1) 
upis <- opa %>% select(colnames(vlg))
#colnames(upis) == colnames(vlg)

ult <- upis*vlg

vlg.loc <- ult[,c(2,3,10:15)]
vlg$local <- rowSums(vlg.loc)
vlg.land <- ult[, c(9,16:21)]
vlg$land <- rowSums(vlg.land)

ok <- bind_rows(list(High.Specialists = vhs[, c("local", "land")],
               Low.Specialists = vls[, c("local", "land")],
               High.Generalists = vhg[, c("local", "land")],
               Low.Generalists = vlg[, c("local", "land")]),
          .id="model") %>%
  separate(model, c("matrix", "habitat")) %>% 
  pivot_longer(3:4, names_to = "term",values_to = "estimate") %>%
  mutate(habitat = fct_relevel(habitat, "Specialists", "Generalists"),
         term = fct_recode(term, Landscape = "land", 
                           Local = "local")) %>%
  mutate(term = fct_relevel(term, "Local", "Landscape"),
         matrix = fct_relevel(matrix, "High", "Low"))
```

```{r, echo=F}
effects.sp<- ok %>%
ggplot(aes(x=estimate, y=matrix, fill=matrix, col=matrix))+
  geom_violin(alpha=0.3)+
  geom_boxplot(width=0.1,, alpha=0.3) +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(cols= vars(term), rows=vars(habitat), switch = "y") +
  scale_fill_manual(name="  Matrix \n  quality ",
                     values=c("darkgreen", "sandybrown")) +
  scale_color_manual(name="  Matrix \n  quality ",
                    values=c("darkgreen", "sandybrown")) +
  theme(text = element_text(size=12),
        axis.text = element_text(size=12),
        strip.text.x = element_text(size=12, margin=margin(t=2,b=3)),
        strip.text.y = element_text(size=12, margin=margin(r=2,l=3)),
        legend.position = c(0.89, 0.2),
        plot.title = element_text(hjust = 0.5),
        legend.box.background = element_rect(fill="snow2", color="snow2"),
        axis.text.y = element_blank(),
        axis.line.y = element_blank(),
        axis.ticks.y = element_blank()) +
  ylab("") +
  xlab("Effect size") +
  ggtitle("Forest cover")
effects.sp
```


```{r, echo=F,results="hide"}
jpeg("figures/forest_cover_effectsize_perSP.jpg", width=16, height = 10, units="cm", res=150)
effects.sp
dev.off()
```



# Trait importance metric

The importance of the trait in explaining habitat loss filtering was calculated using the proportional decrease in the variance of the species random slope of forest cover ($d_{spp[i]$) when you include the trait-environment interaction term ($\beta_{12}$) in the model (Jamil et al. 2013):

$$C_\beta = 1 = \frac{d_{spp[i]}(res)}{d_{spp[i]}(total)}$$




where $d_{spp[i]}(res)$ is the variance of the random slope from model with trait main effects ($\beta_{2}$) and the trait-environment interaction ($\beta_{12}$), and $d_{spp[i]}(total)$ is the same variance term for the model without trait-environment interaction but with the main effects of traits.This proportion explains how much of the effect of habitat loss on each species can be explained by their trait values.

**OBS:** Models without trait*enviroment interaction for the separate traits were previoulsy analyzed in the Rmd scrit `3_modeling_traits_separate.Rmd`.

Models without trait*enviroment interactions for the combined traits:

```{r, eval=F}
mhigh.spe2 <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400 + forest_land +
                    lbody_size + 
                    nest +
                    diet + 
                    lower_stratum +
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=high.spe,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))


mlow.spe2 <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400 + forest_land +
                    lbody_size + 
                    nest +
                    diet + 
                    lower_stratum +
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=low.spe,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))


mhigh.gen2 <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400 + forest_land +
                    lbody_size + 
                    nest +
                    diet + 
                    lower_stratum +
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=high.gen,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))


mlow.gen2 <- glmer(cbind(occor, n.visit-occor) ~  
                    forest_site400 + forest_land +
                    lbody_size + 
                    nest +
                    diet + 
                    lower_stratum +
                    (forest_site400 + forest_land|sp) + 
                    (1|landscape:sp) + (1|site:sp) + 
                    (lbody_size + nest + diet + lower_stratum|landscape) +
                    (lbody_size + nest + diet + lower_stratum|site),
                    family=binomial, data=low.gen,
                    nAGQ = 1, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 500000)))
```

Function to calculate trait importance:
```{r}
cbeta <- function(m.inter, m.no.inter){
    cbeta <- 1-((VarCorr(m.inter)$sp[2,2] + VarCorr(m.inter)$sp[3,3])
               /(VarCorr(m.no.inter)$sp[2,2] + VarCorr(m.no.inter)$sp[3,3]))
  return(round(100*cbeta))
}
```

```{r}
comb <- c(cbeta(mhigh.spe, mhigh.spe2),
          cbeta(mlow.spe,  mlow.spe2),
          cbeta(mhigh.gen, mhigh.gen2),
          cbeta(mlow.gen,  mlow.gen2))

bd   <- c(cbeta(bodyhigh.spe, bodyhigh.spe2),
          cbeta(bodylow.spe,  bodylow.spe2),
          cbeta(bodyhigh.gen, bodyhigh.gen2),
          cbeta(bodylow.gen,  bodylow.gen2))

ni   <- c(cbeta(nesthigh.spe, nesthigh.spe2),
          cbeta(nestlow.spe,  nestlow.spe2),
          cbeta(nesthigh.gen, nesthigh.gen2),
          cbeta(nestlow.gen,  nestlow.gen2))

di   <- c(cbeta(diethigh.spe, diethigh.spe2),
          cbeta(dietlow.spe,  dietlow.spe2),
          cbeta(diethigh.gen, diethigh.gen2),
          cbeta(dietlow.gen,  dietlow.gen2))

ls   <- c(cbeta(low_strathigh.spe, low_strathigh.spe2),
          cbeta(low_stratlow.spe,  low_stratlow.spe2),
          cbeta(low_strathigh.gen, low_strathigh.gen2),
          cbeta(low_stratlow.gen,  low_stratlow.gen2))

st   <- c(cbeta(stratumhigh.spe, stratumhigh.spe2),
          cbeta(stratumlow.spe,  stratumlow.spe2),
          cbeta(stratumhigh.gen, stratumhigh.gen2),
          cbeta(stratumlow.gen,  stratumlow.gen2))

fr   <- c(cbeta(frugihigh.spe, frugihigh.spe2),
          cbeta(frugilow.spe,  frugilow.spe2),
          cbeta(frugihigh.gen, frugihigh.gen2),
          cbeta(frugilow.gen,  frugilow.gen2))

is   <- c(cbeta(insehigh.spe, insehigh.spe2),
          cbeta(inselow.spe,  inselow.spe2),
          cbeta(insehigh.gen, insehigh.gen2),
          cbeta(inselow.gen,  inselow.gen2))
```

```{r}
tra <- data.frame(matrix = c("High quality", "Low quality", 
                             "High quality", "Low quality"),
                  habitat = c("Specialists", "Specialists",
                              "Generalists","Generalists"),
                  comb, ni, di, st, is, fr, ls, bd)
colnames(tra)[3:10] <- c("Combined","Nest type", "Main diet", 
        "Foraging stratum", "% insectivory", "% frugivory", "% lower strata",
                             "Body mass")
tra
```

```{r}
figtrait.env <- tra %>% gather("trait", "value", 3:10) %>%
  mutate(trait = fct_relevel(trait, "Combined","Nest type", "Main diet", 
                             "Foraging stratum", "% insectivory", "% frugivory", 
                             "% lower strata",
                             "Body mass"),
         habitat = fct_relevel(habitat, "Specialists", "Generalists")) %>% 
  arrange(trait) %>%
  mutate(xis=rep(1:8, each=4)) %>%
  ggplot(aes(x=xis, y=value, col=matrix)) + geom_line(size=1) + geom_point(size=3) +
  facet_grid(~habitat) +
  scale_x_continuous(breaks=1:8, labels= c("Combined","Nest type", "Main diet", 
                                           "Foraging stratum", "% insectivory", "% frugivory", "% lower strata",
                                           "Body mass")) +
  xlab("") +
  scale_color_manual(name="Matrix \n quality",
                     labels = c("High", "Low"),
                     values = c("darkgreen", "sandybrown")) +
  ylab("Trait importance (%)")+
  theme(axis.text.x = element_text(angle=45, hjust=1),
        text = element_text(size=12),
        axis.text = element_text(size=12),
        legend.box.background = element_rect(fill="snow2", color="snow2"),
        strip.text = element_text(size=12, margin=margin(t=2,b=3)),
        legend.justification = c(1, 0), legend.position = c(1, 0.65)) 
figtrait.env
```

```{r, eval=F}
jpeg("figures/fig_traitXenv.jpg", width=20, height = 12, units="cm", res=150)
figtrait.env
dev.off()
```

# R^2^ models

```{r}
traits = c("lbody_size", "nest", "diet", "lower_stratum")
vals <- bind_rows(list(High_Specialists = r2.calc(mhigh.spe, atrib=traits)*100,
      Low_Specialists=r2.calc(mlow.spe, atrib=traits)*100,
      High_Generalists=r2.calc(mhigh.gen, atrib=traits)*100,
     Low_Generalists=r2.calc(mlow.gen, atrib=traits)*100), .id="assemblage")

colnames(vals) <- c("assemblage", "condicional", "trait*env", "env|sp", "lands:sp", "site:sp", "trait|lands", "trait|site")

vals2 <-  vals %>%
  separate(assemblage, c("matrix", "habitat")) %>%
  select(-condicional) %>%
  pivot_longer(3:8, names_to = "term", values_to = "R2") %>%
  mutate(term = fct_relevel(term,"trait|site", "trait|lands", "site:sp", 
                                  "lands:sp", "trait*env","env|sp"),
         habitat = fct_relevel(habitat, "Specialists", "Generalists"),
         matrix = fct_relevel(matrix, "Low", "High")) %>%
  arrange(habitat,matrix,desc(term)) %>%
  group_by(habitat, matrix) %>%
  mutate(yis = cumsum(R2)-R2/2, 
         label = as.character(round(R2))) %>% ungroup() %>%
  mutate(xis = rep(rep(c(1.31,2.31), each=6), 2))

fig.part <- ggplot(vals2, aes(x=matrix, y=R2, fill=term)) + geom_col(width=0.7) +
  scale_fill_manual(name="Model terms" ,
                    values = c("lightgrey","darkgrey","aquamarine1",
                               "aquamarine3", "slateblue1", "slateblue4")) +
  facet_wrap(~habitat)+
  scale_y_continuous(name= expression(~ R^2), breaks=seq(0,70,10),
                     limits=c(0,75)) +
  scale_x_discrete(name="Matrix quality") +
  theme(text = element_text(size=12),
        axis.text = element_text(size=12),
        strip.text = element_text(size=12, margin=margin(t=2,b=3))) +
geom_text_repel(data=vals2, aes(label=label, y=yis, x=xis), 
                segment.size = 0.15, size=3,
                segment.alpha = 0.7,
                direction="y",
                show.legend=F,   nudge_x = 0.15, hjust=0)

fig.part
```


```{r, eval=F}
jpeg("figures/fig_R2.jpg", width=20, height = 12, units="cm", res=150)
fig.part
dev.off()
```


# Saving models results

```{r, eval=F}
save(mhigh.gen, mhigh.spe, mlow.gen, mlow.spe,
     mhigh.gen2, mhigh.spe2, mlow.gen2, mlow.spe2,
  file="models_outputs/models_combined.Rdata")
```

